% Start writing your answer from here, if you want to use new packages/change something do it in main.tex
\begin{que}
	Imagine an infinitely long line of traders waiting outside a brokerage
	firm to place their trades. Each trader is assigned an ID number from 1
	to 200 (both inclusive, obviously these IDs are not unique). The firm’s
	director announces a special offer: the first trader in the queue whose
	ID number matches the ID of any trader who has already placed a trade
	will receive a free trade (i.e., a trade without any margins). You have
	the option to choose your position in this queue.   However, you don’t
	know the ID numbers of the traders ahead of you or behind you. Your
	goal is to maximize your chances of being the first trader whose ID
	matches someone who has already placed a trade. Given this situation,
	what position in the queue should you choose to maximize your chances
	of receiving the free trade?
	\hspace*{\fill} [6 marks]
\end{que}
\begin{tcolorbox}[breakable]
	\begin{sol}
		\textbf{Note:} To run the code for this, execute \texttt{python3 ./code/q5.py}.

		We have infinite number of trader where each trader is assigned
		an ID number from 1 to 200 waiting in a queue. We need to find
		the position which maximises the chance of getting a free
		trade, where free trade is awarded to a person whose ID number
		matches with someone ahead in the queue, that is, person who
		has traded. Since there are 200 unique IDs, the last position
		one can win is 201 (by pigeon hole principle). 1st person can
		never win as it has no one ahead of him. Therefore for $i^{th}$
		person $i \in \{2,3,4,\cdots,201 \}$ to win, the probability of
		winning a free trade is given by
		\begin{align}
			P(i) & = \frac{200}{200} \times \frac{199}{200} \times \cdots \times \frac{202 - i}{200} \times \frac{i-1}{200} \\
			     & = \prod_{j=2}^{i} \Bigg( \frac{202 - j}{200} \Bigg) \times \frac{i - 1}{200}
		\end{align}

		The probability is derived by the logic that if $i^{th}$ person
		is going to win, then all of the people ahead him need to loose
		and ith person has i-1 choices to secure victory. For maximising
		this probability I have used python and I have attached a file
		for the code. The position which maximises the probability of
		winning a free trade is 15 with a probability of 0.0439.

	\end{sol}
\end{tcolorbox}
