% Start writing your answer from here, if you want to use new packages/change something do it in main.tex

\begin{que}
	You are playing a trading game against two teams $A$ and $B$ (will
	happen in reality soon). The game is played in the form of a three-set
	series with $A$ and $B$ alternately. Also, Team $B$ is better at
	trading than Team $A$. To encourage your trading career, the exchange
	(an organization responsible for managing the trades) gives you two
	options $A$-$B$-$A$ (which means you play a game with Team $A$, then
	Team $B$ and at last Team $A$ again) or $B$-$A$-$B$. You will win if
	you win two sets in a row. Which of the two options should you choose?
	Justify your choice with proper calculations.
	\hspace*{\fill} [5 marks]
\end{que}

\begin{tcolorbox}[breakable]
	\begin{sol}
		Let $p_A$ and $p_B$ be the probability of winning the set
		against Team $A$ and Team $B$ respectively. Since, Team $B$ is
		better than team $A$, we know that,
		\begin{align}
			p_A>p_B
		\end{align}

		For the first sequence, (i.e. $A-B-A$), to result in a win, we
		either have to win first and second set and lose the third set,
		or win the second and third set and lose the first set win all
		three sets. Probability of this happening is, (denoted as
		$P_1$)
		\begin{align}
			P_1=p_A\cdot p_B \cdot (1-p_A)+(1-p_A)\cdot p_B\cdot p_A +p_A\cdot p_B\cdot p_A
		\end{align}
		\begin{align}
			P_1=p_Ap_B-p_A^2p_B+p_Ap_B-p_A^2p_B+p_A^2p_B
		\end{align}
		\begin{align}
			P_1=2p_Ap_B-p_A^2p_B
		\end{align}

		Similary for second sequence, (i.e, $B-A-B$), the probablity for
		winning will be (let it be $P_2$)
		\begin{align}
			P_2=p_B\cdot p_A \cdot (1-p_B)+(1-p_B)\cdot p_A\cdot p_B +p_B\cdot p_A\cdot p_B
		\end{align}
		\begin{align}
			P_2=p_Ap_B-p_Ap_B^2+p_Ap_B-p_Ap_B^2+p_Ap_B^2
		\end{align}
		\begin{align}
			P_2=2p_Ap_B-p_Ap_B^2
		\end{align}

		Since we know that,
		\[p_A>p_B\]
		As, both $p_A$ and $p_B$ is positive, we can multiple them to
		both the sides without changing the inequality sign,
		\begin{align}
			p_A\cdot p_Ap_B > p_B\cdot p_Ap_B
		\end{align}

		This gives us:
		\begin{align}
			p_A^2p_B > p_Ap_B^2
		\end{align}

		Multiplying $-1$ on both the sides,
		\begin{align}
			-p_A^2p_B < -p_Ap_B^2
		\end{align}

		Adding $2p_Ap_B$ on both the sides,
		\begin{align}
			2p_Ap_B-p_A^2p_B < 2p_Ap_B-p_Ap_B^2
		\end{align}

		Which simplifies to,
		\begin{align}
			P_1 < P_2
		\end{align}

		So, playing in the \textbf{second} sequence ($B-A-B$) gives us
		better chances of winning the game.
	\end{sol}
\end{tcolorbox}
